Implementation of a stable, high-power optical lattice for quantum gas microscopy

### 2019-01-27 LatticeOptics/submission_rev_sci_inst_revised/latticeoptics.tex
Updated referee comments

To achieve the desired functionality, the final op-amp stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by including a fast Schottky diode (ON Semiconductor BAT54S) in the feedback arm.
This can be seen by considering two extreme cases: far below the diode drop, the diode is an open circuit and the gain is set by $R_l$; above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.
Naturally, the voltage drop across the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode (\unit{3.3}{V}).
Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in Fig.~\ref{fig:bandwidth}.
Were it not for the linearization, the gain of the mixer would change by a factor of 10 over a dynamic range spanning two orders of magnitude.
The loop transfer function is sensitive to the specific tuning parameters of the nonlinear controller resulting in slightly different transfer functions for the two axes, although both exhibit approximately constant behavior over the desired range of setpoints.
Another function of the last stage is to clamp the voltage to be strictly positive by including a diode clamp on the output to prevent unstable positive feedback behavior~\cite{Horowitz2015}.
Finally, since the mixer is a current driven device, the last stage of the feedback loop uses the low-noise OPA627 (Texas Instruments) op-amp which is able to supply tens of mA of current into an output impedance of \unit{50}{\Omega}.

>>>>

To achieve the desired functionality, the final op-amp stage linearizes the response by increasing the gain at low signal levels and suppressing it at high signal levels by including a fast Schottky diode (ON Semiconductor BAT54S) in the feedback arm.
This can be seen by considering two extreme cases: far below the diode drop, the diode is an open circuit and the gain is set by $R_l$; above the diode drop it is a closed circuit where the gain is set by the resistor $R_h$.
Naturally, the voltage drop across the diode is chosen such that it is approximately half the maximum desired signal level of the photodiode (\unit{3.3}{V}).
Although a large improvement, the bandwidth still varies over the dynamic range of the loop, but only by approximately a factor of two, as seen in Fig.~\ref{fig:bandwidth}.
Were it not for the linearization, the gain of the mixer would change by a factor of 10 over a dynamic range spanning two orders of magnitude.
The loop transfer function is sensitive to the specific tuning parameters of the nonlinear controller resulting in slightly different transfer functions for the two axes, although both exhibit approximately constant behavior over the desired range of setpoints.
Another function of the last stage is to clamp the voltage to be strictly positive by including a diode clamp on the output to prevent unstable positive feedback behavior~\cite{Horowitz2015}.
Finally, since the mixer is a current driven device, the last stage of the feedback loop uses the low-noise OPA627 (Texas Instruments) op-amp which is able to supply tens of mA of current into an input impedance of \unit{50}{\Omega}.
